Assigning Scouts to Optimal Patrols

### 2016-06-08 draft1.tex

\section*{Mathematical Model}
To model the relationships between scouts, we use a mathematical graph. A graph is a convenient way to illustrate direct relationships between pairs of objects; for example, if we have a collection of cities in a state, a city can be related to another if there is a direct path between them. A city can be considered a vertex, and two cities can have a edge between them if there is a direct path connecting them. Edges can have weights attached to them such as the distance between the two cities. The edges can even be directed in which the distance from City A to City B might be different with the distance from City B to City A. Graphs can also be complete if each vertex in a graph is connected to every other vertex. Graphs are not limited to just cities on a map, but rather a collection of objects with any notion of relationship can be represented as a graph.

@@

\section*{Verification Statement}
(Once we receive our verification statement, we will place it here.)

\section*{Appendix A}
The other objective functions.

>>>>

\section*{Mathematical Model}
To model the relationships between scouts, we use a mathematical graph. A graph is a convenient way to illustrate direct relationships between pairs of objects; for example, if we have a collection of cities in a state, a city can be related to another if there is a road between them. A city can be considered a vertex, and two cities can have a edge between them if there is a road connecting them. Edges can have weights attached to them such as the length of the road between the two cities. The edges can even be directed, meaning that distance from City A to City B might be different with the distance from City B to City A (two one-way roads may have different lengths). Graphs can also be complete if each vertex in a graph is connected to every other vertex. Graphs are not limited to just cities on a map, but rather a collection of objects with any notion of relationship can be represented as a graph.

@@

\section*{Verification Statement}
Scoutmaster Gene Bruce addressed our professor, Sara Billey, with the following comments: ``I'd like to thank you and your students for developing a process to divide a group of new scouts into patrols based upon solicited personal preferences.  While a relatively small problem, it can take a lot of effort to solve by hand.  The students grasped the subtleties of the conflicting objectives.  I appreciated their approach of using multiple objective functions.  This provided a family of solutions that gave insights into the problem.  I appreciate this much more than a process that produces the ``one best answer".  It's much easier for me to add my ``gut instinct" with a handful of alternatives rather than the original 1716 possible combinations.  I look forward to setting up the process on my home computer and leveraging it during the next recruiting season."
\section*{Appendix A}
The other objective functions.
